%-------------------------
% Resume in Latex
% Author : Neel Bhansali
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
        \textbf{\Huge\scshape Neel Bhansali} \\ \vspace{2pt}
    \small 
    \href{https://neelbhansali.com}{\underline{\textbf{neelbhansali.com}}} $|$
    \href{https://github.com/neel-bhan}{\underline{github.com/neel-bhan}} $|$
    \href{https://www.linkedin.com/in/neel-bhansali-506a42265/}{\underline{linkedin.com/in/neel-bhansali}} $|$
    \href{mailto:neelbh99@gmail.com}{\underline{neelbh99@gmail.com}} $|$
    817-659-4024
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Wisconsin Madison}{Madison, Wisconsin}
      {Bachelor of Science in Computer Science, Data Science \textbf{GPA:3.73}}{Expected Graduation 2028}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart


      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
\resumeSubheading
{Software Engineer Intern}{June 2026 -- Aug 2026}
{DraftKings}{Boston, MA}
\resumeItemListStart
\resumeItem{Built a .NET service for a server-driven UI platform to validate, version, and serve dynamic CMS templates.}
\resumeItem{Developed a drag-and-drop Template Builder that converts visual layouts into schema-valid JSON, validates templates upfront, persists version history, and feeds the live rendering pipeline.}
\resumeItem{Implemented a Claude-powered agentic workflow to generate validated CMS templates from prompts.}
\resumeItemListEnd

\resumeSubheading
    {Software Engineer Intern}{Sept 2025 -- Present}
    {Represented Collective}{Madison, WI}
    \resumeItemListStart
        \resumeItem{Developed a HIPAA-compliant mobile health application for asthma patients using React Native (Expo)}
        \resumeItem{Engineered a Express.js, Prisma, PostgreSQL backend, containerized with Docker, deployed on AWS ECS/RDS, featuring JWT-based access control, audit logging, and strict validation pipelines.}
        \resumeItem{Implemented symptom tracking, medication adherence logging, and analytics dashboards.}
    \resumeItemListEnd
\resumeSubheading
    {Software Engineer Intern}{June 2025 -- Aug 2025}
    {Mini Orange}{Dallas, TX}
    \resumeItemListStart
        \resumeItem{Designed and implemented features for a secure, web-based Active Directory management platform, enabling enterprise-scale user/group/OU administration, audit logging, and MFA-enabled self-service password resets.}
        \resumeItem{Created React frontend with dynamic forms, organizational management modules, and configurable CAPTCHA, improving operational efficiency and reducing admin configuration time.}
        \resumeItem{ Built fault-tolerant .NET REST APIs with advanced error handling and monitoring pipelines.}
    \resumeItemListEnd

    \resumeSubheading
    {Research Assistant}{May 2022 -- July 2022}
    {University of Texas at Dallas}{Richardson, TX}
    \resumeItemListStart
        \resumeItem{Gained in-depth knowledge of AI/ML techniques including NN, CNNs, LSTMs, SVMs, RL, and Decision Trees.}
\resumeItem{Developed a face recognition system using machine learning to enhance University security infrastructure.}
        \resumeItem{Performed data cleaning, feature engineering, and hyperparameter tuning with Pytorch to optimize models.}
        
        
    \resumeItemListEnd
% \item \textbf{Academic Tutor, Eye Level Learning Center} \hfill Jan 2023 -- Current \\
% Directed tutoring for 3rd–12th grade students, creating plans and collaborating with teachers to drive growth.
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects \& Leadership}
    \resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{College Resale Platform} }{May 2025 -- Aug 2025}
    \resumeItemListStart
        \resumeItem{Built a university-exclusive marketplace focused on resale of textbooks and sports tickets, with automated school email verification, geolocation search, and web scraping to list real-time campus sporting events.}
        \resumeItem{Architected and deployed a full-stack platform with React.js, TypeScript, Vite, Tailwind CSS for responsive UI and Node.js, Express.js, PostgreSQL backend (JWT auth, REST APIs), running on AWS (S3 for image storage + frontend hosting, RDS for PostgreSQL, ECS + Fargate for backend containers, VPC networking).}
        \resumeItem{Engineered real-time chat and notifications via WebSockets enabling instant bidding and live ticket updates.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Agentic Portfolio Updater} }{Aug 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Built an agentic AI pipeline that detects new GitHub repos via webhooks, generates project summaries with the OpenAI API, and submits PRs updating a Next.js/React portfolio site for seamless portfolio integration.}
    \resumeItem{Designed a structured JSON/YAML schema for consistent project entries with automated tech stack detection and tagging, supporting scalable updates across projects; integrated README image parsing for project previews}
    \resumeItem{Implemented AWS SQS, Lambda, S3 and GitHub Actions CI/CD with rollbacks, and PR validation.}
  \resumeItemListEnd

\resumeProjectHeading
    {\textbf{AIFA (AI FOR ALL)} }{September 2022 -- Present}
  \resumeItemListStart
    \resumeItem{Developed comprehensive AI-centric educational modules and facilitated interactive workshops AI concepts}
    \resumeItem{Organized hackathons with 200+ students, \$2000+ prizes, and sponsors including Google, GitHub, and Keurig.}
  \resumeItemListEnd

% \resumeProjectHeading
%     {\textbf{Workout Generator}}{Aug 2024 -- Oct 2024}
%     \resumeItemListStart
%         \resumeItem{Developed a personalized workout generator using decision tree algorithms to recommend routines tailored to user inputs such as age, gender, fitness goals, and target muscle groups.}
%         \resumeItem{Designed an interactive dashboard to let users adjust preferences and receive updated workout plans in real time.}
%     \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages \& Cloud}{: Java, Python, JavaScript/TypeScript, C\#, SQL, AWS (Lambda, S3, ECS, RDS, VPC, Fargate)} \\
        \textbf{Frameworks \& Libraries}{: React, Node.js, Express, Tailwind CSS, PyTorch, Pandas, NumPy} \\
        \textbf{Databases \& Tools}{: PostgreSQL, MongoDB, OpenAI API, Docker, Git, GitHub Actions, APIs, WebSockets, JWT}
    }}
\end{itemize}

%-------------------------------------------
\end{document}